---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mbr

<!-- badges: start -->
[![R build status](https://github.com/mdsumner/mbr/workflows/R-CMD-check/badge.svg)](https://github.com/mdsumner/mbr/actions)
<!-- badges: end -->

The goal of mbr is to compute the minimum bounding rectangle of a set of points. 

Provided as an answer to a question on this site, by Bill Huber on 2012-04-05

https://gis.stackexchange.com/questions/22895/finding-minimum-area-rectangle-for-given-points/22934?stw=2#22934

Here is an example of its use:

```{r mbr}  
library(mbr)
  # Create sample data
  set.seed(23)
p <- matrix(rnorm(20*2), ncol=2)                 # Random (normally distributed) points
mbr <- MBR(p)

# Plot the hull, the MBR, and the points
limits <- apply(mbr, 2, range) # Plotting limits
plot(p[(function(x) c(x, x[1]))(chull(p)), ], 
     type="l", asp=1, bty="n", xaxt="n", yaxt="n",
     col="Gray", pch=20, 
     xlab="", ylab="",
     xlim=limits[,1], ylim=limits[,2])                # The hull
lines(mbr, col="Blue", lwd=3)                         # The MBR
points(p, pch=19)    

```

## Installation

You can install with

``` r
remotes::install_github("mdsumner/mbr"
```


## sf

For an sf wrapper see https://github.com/mdsumner/mbr/issues/1

## Code of Conduct
  
Please note that the mbr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
